On the probability of finding nonphysical solutions through shadowing\tnoteref{1}

### 2021-04-23 letter/responseToReviewers.tex

We thank the reviewer for pointing out multiple references that support the conclusions of the present paper. In our revised manuscript, we have added them to our discussion section 5 (the edits are highlighted in \reviewerOne{red}), where we had originally referred to Clean Numerical Simulation (CNS).

2. \reviewerOne{There is another thing that might be mentioned.  Periodic solutions of some chaotic systems, such as three-body system, have physical meanings.  Although three-body systems are chaotic in essence, periodic orbits of three-body system indeed exist.}

Thank you for pointing this important point out. In our paper, we use ``nonphysicality'' to mean ``atypicality'' in the following sense, which, as you point out, may not be physically meaningless. Whenever an initial condition is sampled from a set of full Lebesgue measure in an open set, known as the attractor basin, that contains the chaotic attractor, the ergodic average along the orbit starting from that initial condition is equal to the ensemble average. This latter ensemble average or phase-space average is with respect to an SRB-type probability measure, which is called a {\em physical} measure (Ref. 10) since it is ``observed'' through ergodic averages along almost every orbit starting in the attractor basin. Thus, we refer to as ``nonphysical'' atypical orbits that do not produce the correct statistics associated with the SRB measure.

Nevertheless, as you point out, in some problems, such as the three-body problem, families of periodic orbits have been observed and studied in their own right \cite{henon3body}. Furthermore, the collection of unstable periodic orbits is intimately connected with the statistical properties of the strange attractor. Ensemble averages can be realized as weighted ergodic averages along long unstable periodic orbits (e.g. see Property 3.10 of \cite{llave}). Dynamical determinants, which are calculated on the set of periodic orbits, are connected with spectral resonances or the slowest correlation decay rates \cite{baladi-book}. Apart from these theoretical connections, the set of unstable periodic orbits is also recognized as a physically interpretable ``skeleton'' of an attractor \cite{cvitanovic1}. Besides providing alternative methods to calculate dynamical properties, the tangencies on unstable periodic orbits are thought to play an important role in attractor crises: a large statistical response to small system parameter perturbations \cite{berry}\cite{grebogi1}.

### 2021-04-23 letter/summaryOfRevisions.tex
Add few more refs and complete writing on periodic orbits

\begin{center}
		\Large{\textbf{Manuscript JCOMP-D-20-01958: Response to Reviewers}}
\end{center}
\medskip
We would first like to thank both the reviewers for investing their time to read our work carefully and provide us with thoughtful feedback. We have revised our work to incorporate all of both the reviewers' suggestions. Here is a summary of the changes we have made:
\begin{itemize}
    \item We have added citations to works pointed out to us by Reviewer 1 that strengthen the conclusions of this paper, especially on the implications of our results for the statistical inaccuracy of numerical solutions to chaotic systems. A brief explanation of the cited works is added to section 5, and is highlighted in \reviewerOne{red}.
    \item We have added a couple of paragraphs in section 3.2 (in \reviewerOne{blue}) to explain the sense in which we refer to periodic solutions as nonphysical. This is in response to a comment by Reviewer 1 on periodic solutions having physical interpretations.
    \item 
\end{itemize}
\end{document}

>>>>

\begin{center}
		\Large{\textbf{Manuscript JCOMP-D-20-01958: Summary of changes}}
\end{center}
\medskip
We would first like to thank both the reviewers for investing their time to read our work carefully and provide us with thoughtful feedback. We have revised our work to incorporate all of both the reviewers' suggestions. Here is a summary of the changes we have made:
\begin{itemize}
    \item We have added citations to works pointed out to us by Reviewer 1 that strengthen the conclusions of this paper, especially on the implications of our results for the statistical inaccuracy of numerical solutions to chaotic systems. A brief explanation of the cited works is added to section 5, and is highlighted in \reviewerOne{red}.
    \item We have added a couple of paragraphs in section 3.2 (in \reviewerOne{blue}) to explain the sense in which we refer to periodic solutions as nonphysical. This is in response to a comment by Reviewer 1 on periodic solutions having physical interpretations.
    \item We have provided a detailed answer to Reviewer 2's question in the response to Reviewers on the interpretation of numerical solutions to chaotic systems. We have included some of this clarification also in section 5 of the revised manuscript in \reviewerTwo{red}.
    \item We have changed the ``L''s and ``R''s in the figure captions to ``left''s and ``right''s respectively.
\end{itemize}
\end{document}

### 2021-04-23 main_els.tex
Add few more refs and complete writing on periodic orbits

\reviewerOne{
At the same time, the set of all periodic solutions is a dense subset of the attractor. That is,}

Figure \ref{fig:lorenz_periodic} shows
a few periodic solutions of the Lorenz equation. Comparing these solutions
to the physical solution visualized in Figures \ref{fig:lorenz_ergodicity1}--\ref{fig:lorenz_ergodicity3},
we see that the periodic solutions are significantly more limited in their
extent of exploration.

>>>>

\reviewerOne{
At the same time, families of periodic solutions have been well-studied for some problems}\cite{henon3body}.\reviewerOne{The set of all unstable periodic orbits have been recognized as the ``skeleton'' of the chaotic attractor \cite{cvitanovic1} forming a dense subset of the attractor and providing an alternative characterization of the SRB distribution \cite{llave}. This implies that ergodic/ensemble averages with respect to the SRB distribution are also weighted averages along unstable periodic orbits.} \reviewerOne{The significance of the set of unstable periodic orbits extends even further as it can be used to compute dynamical invariants such as entropy and Lyapunov dimension \cite{grebogi1}\cite{cvitanovic1}. A quantity of great mathematical interest is the dynamical determinant (see \cite{baladi-book} for a recent review), which is computed as a weighted sum over all periodic orbits. The zeros of the dynamical determinant have a one-to-one correspondence with the slowest decay rates of correlations between observables \cite{ruelleDeterminant}. This connection has been exploited both in mathematical as well as physical studies of the distribution of energy levels and resonances in quantum scattering \cite{semyonZworksi}\cite{berry}\cite{cvitanovic2005chaos}. Furthermore, theoretical and numerical studies have attributed cataclysmic changes in the shape and position of the attractor in response to small parameter changes, known as attractor crises \cite{grebogi1}, to the emergence of tangencies between the stable and unstable manifolds along periodic orbits.}
Figure \ref{fig:lorenz_periodic} shows
a few periodic solutions of the Lorenz equation. Comparing these solutions
to the physical solution visualized in Figures \ref{fig:lorenz_ergodicity1}--\ref{fig:lorenz_ergodicity3},
we see that the periodic solutions are significantly more limited in their
extent of exploration.
